---
title: "Sourcebook Dashboard - Markdown Version"
---

## {.sidebar}

```{r}
#| echo: false

library(bslib)
library(bsicons)
library(htmltools)
library(shiny)

# Complete sidebar content in proper order
tagList(
  # Header with logo and branding - at the very top
  div(
    class = "sidebar-header",
    style = "padding: 1.5rem 1.5rem 1rem; border-bottom: 1px solid rgba(255, 255, 255, 0.1); margin-bottom: 1rem;",

    # Clickable logo/title for home
    tags$a(
      href = "#intro-page",
      `data-subpage` = "intro-page",
      style = "text-decoration: none; cursor: pointer;",
      div(
        style = "text-align: center; margin-bottom: 0.75rem; background-color: rgba(255, 255, 255, 0.95); border-radius: 8px; padding: 0.75rem; margin: 0 1rem 0.75rem 1rem; transition: all 0.2s ease;",
        class = "home-link",
        img(src = "www/hfv_rgb_logo.png", style = "height: 50px; max-width: 100%; object-fit: contain;")
      ),
      div(
        style = "text-align: center; color: white; font-weight: 700; font-size: 1.4rem; letter-spacing: 1px; margin-top: 0.5rem; transition: all 0.2s ease;",
        class = "home-title",
        "SOURCEBOOK"
      )
    ),

    # Social icons
    div(
      style = "text-align: center; margin-top: 0.75rem;",
      div(
        style = "display: flex; justify-content: center; gap: 0.75rem;",
        tags$a(
          href = "https://housingforwardva.org",
          target = "_blank",
          title = "HousingForward Virginia Website",
          style = "color: rgba(255, 255, 255, 0.7); text-decoration: none; transition: all 0.2s ease; padding: 0.25rem;",
          class = "social-icon",
          bsicons::bs_icon("globe", size = "1.1em")
        ),
        tags$a(
          href = "https://twitter.com/housingforwardva",
          target = "_blank",
          title = "Follow us on Twitter",
          style = "color: rgba(255, 255, 255, 0.7); text-decoration: none; transition: all 0.2s ease; padding: 0.25rem;",
          class = "social-icon",
          bsicons::bs_icon("twitter-x", size = "1.1em")
        ),
        tags$a(
          href = "https://www.linkedin.com/company/housingforwardva/",
          target = "_blank",
          title = "Connect on LinkedIn",
          style = "color: rgba(255, 255, 255, 0.7); text-decoration: none; transition: all 0.2s ease; padding: 0.25rem;",
          class = "social-icon",
          bsicons::bs_icon("linkedin", size = "1.1em")
        )
      )
    )
  ),

  # Custom Geographic Selection with Toggle Buttons
  div(
    style = "margin-bottom: 20px; padding: 0 1.5rem;",

    # Label for geographic selection
    tags$label("View data for:", class = "geo-selector-label"),

    # Custom toggle button group
    div(
      class = "geo-toggle-group",
      style = "margin-bottom: 1rem;",
      tags$button(
        class = "geo-toggle-btn active",
        `data-value` = "state",
        id = "btn-state",
        "Virginia State"
      ),
      tags$button(
        class = "geo-toggle-btn",
        `data-value` = "cbsa",
        id = "btn-cbsa",
        "Metro Area"
      ),
      tags$button(
        class = "geo-toggle-btn",
        `data-value` = "locality",
        id = "btn-locality",
        "Locality"
      )
    ),

    # Hidden input to maintain Shiny compatibility
    tags$input(
      type = "hidden",
      id = "geo_level",
      name = "geo_level",
      value = "state"
    )
  ),

  # CBSA Selector (JavaScript-controlled visibility)
  div(
    id = "cbsa-selector-container",
    class = "geo-selector-container",
    style = "margin-bottom: 15px; padding: 0 1.5rem; display: none;",
    tags$label("Select Metro Area:", class = "geo-selector-label"),
    div(
      class = "custom-dropdown",
      id = "cbsa-dropdown",
      `data-value` = "Richmond, VA",
      tags$div(class = "dropdown-selected", "Richmond, VA"),
      tags$div(class = "dropdown-arrow", "▼"),
      tags$div(
        class = "dropdown-options",
        tags$div(class = "dropdown-option", `data-value` = "Big Stone Gap, VA", "Big Stone Gap, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Blacksburg-Christiansburg, VA", "Blacksburg-Christiansburg, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Bluefield, WV-VA", "Bluefield, WV-VA"),
        tags$div(class = "dropdown-option", `data-value` = "Charlottesville, VA", "Charlottesville, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Danville, VA", "Danville, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Harrisonburg, VA", "Harrisonburg, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Kingsport-Bristol, TN-VA", "Kingsport-Bristol, TN-VA"),
        tags$div(class = "dropdown-option", `data-value` = "Lynchburg, VA", "Lynchburg, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Martinsville, VA", "Martinsville, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Non-Metro", "Non-Metro"),
        tags$div(class = "dropdown-option active", `data-value` = "Richmond, VA", "Richmond, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Roanoke, VA", "Roanoke, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Staunton, VA", "Staunton, VA"),
        tags$div(class = "dropdown-option", `data-value` = "Virginia Beach-Norfolk-Newport News, VA-NC", "Virginia Beach-Norfolk-Newport News, VA-NC"),
        tags$div(class = "dropdown-option", `data-value` = "Washington-Arlington-Alexandria, DC-VA-MD-WV", "Washington-Arlington-Alexandria, DC-VA-MD-WV"),
        tags$div(class = "dropdown-option", `data-value` = "Winchester, VA-WV", "Winchester, VA-WV")
      )
    ),
    # Hidden input for compatibility
    tags$input(type = "hidden", id = "cbsa_selector", name = "cbsa_selector", value = "Richmond, VA")
  ),

  # Locality Selector (JavaScript-controlled visibility)
  div(
    id = "locality-selector-container",
    class = "geo-selector-container",
    style = "margin-bottom: 15px; padding: 0 1.5rem; display: none;",
    tags$label("Select Locality:", class = "geo-selector-label"),
    div(
      class = "custom-dropdown",
      id = "locality-dropdown",
      `data-value` = "Richmond City",
      tags$div(class = "dropdown-selected", "Richmond City"),
      tags$div(class = "dropdown-arrow", "▼"),
      tags$div(
        class = "dropdown-options",
        style = "max-height: 300px; overflow-y: auto;",
        tags$div(class = "dropdown-option", `data-value` = "Accomack County", "Accomack County"),
        tags$div(class = "dropdown-option", `data-value` = "Albemarle County", "Albemarle County"),
        tags$div(class = "dropdown-option", `data-value` = "Alexandria City", "Alexandria City"),
        tags$div(class = "dropdown-option", `data-value` = "Arlington County", "Arlington County"),
        tags$div(class = "dropdown-option", `data-value` = "Charlottesville City", "Charlottesville City"),
        tags$div(class = "dropdown-option", `data-value` = "Chesapeake City", "Chesapeake City"),
        tags$div(class = "dropdown-option", `data-value` = "Chesterfield County", "Chesterfield County"),
        tags$div(class = "dropdown-option", `data-value` = "Fairfax City", "Fairfax City"),
        tags$div(class = "dropdown-option", `data-value` = "Fairfax County", "Fairfax County"),
        tags$div(class = "dropdown-option", `data-value` = "Hampton City", "Hampton City"),
        tags$div(class = "dropdown-option", `data-value` = "Hanover County", "Hanover County"),
        tags$div(class = "dropdown-option", `data-value` = "Henrico County", "Henrico County"),
        tags$div(class = "dropdown-option", `data-value` = "Loudoun County", "Loudoun County"),
        tags$div(class = "dropdown-option", `data-value` = "Newport News City", "Newport News City"),
        tags$div(class = "dropdown-option", `data-value` = "Norfolk City", "Norfolk City"),
        tags$div(class = "dropdown-option", `data-value` = "Portsmouth City", "Portsmouth City"),
        tags$div(class = "dropdown-option", `data-value` = "Prince William County", "Prince William County"),
        tags$div(class = "dropdown-option active", `data-value` = "Richmond City", "Richmond City"),
        tags$div(class = "dropdown-option", `data-value` = "Roanoke City", "Roanoke City"),
        tags$div(class = "dropdown-option", `data-value` = "Stafford County", "Stafford County"),
        tags$div(class = "dropdown-option", `data-value` = "Suffolk City", "Suffolk City"),
        tags$div(class = "dropdown-option", `data-value` = "Virginia Beach City", "Virginia Beach City"),
        tags$div(class = "dropdown-option", `data-value` = "York County", "York County")
      )
    ),
    # Hidden input for compatibility
    tags$input(type = "hidden", id = "locality_selector", name = "locality_selector", value = "Richmond City")
  ),

  # Navigation Section Divider
  hr(style = "margin: 20px 1.5rem; border-color: rgba(255, 255, 255, 0.2);"),

  # Topic Navigation Accordion
  accordion(
  id = "topic_nav",
  open = NULL,

  # Demographics Section
  accordion_panel(
    "Demographics",
    icon = bsicons::bs_icon("people-fill"),
    div(
      a("Total Population",
        href = "#demographics-total-population",
        `data-subpage` = "demographics-total-population"),
      br(),
      a("Race and Ethnicity",
        href = "#demographics-race-ethnicity",
        `data-subpage` = "demographics-race-ethnicity"),
      br(),
      a("Age",
        href = "#demographics-age",
        `data-subpage` = "demographics-age"),
      br(),
      a("Household Type",
        href = "#demographics-household-type",
        `data-subpage` = "demographics-household-type"),
      br(),
      a("Household Size",
        href = "#demographics-household-size",
        `data-subpage` = "demographics-household-size")
    )
  ),

  # Inventory Section
  accordion_panel(
    "Inventory",
    icon = bsicons::bs_icon("house"),
    div(
      a("Housing Production",
        href = "#inventory-housing-production",
        `data-subpage` = "inventory-housing-production"),
      br(),
      a("Housing Type",
        href = "#inventory-housing-type",
        `data-subpage` = "inventory-housing-type"),
      br(),
      a("Housing Age",
        href = "#inventory-housing-age",
        `data-subpage` = "inventory-housing-age"),
      br(),
      a("Housing Characteristics",
        href = "#inventory-housing-characteristics",
        `data-subpage` = "inventory-housing-characteristics"),
      br(),
      a("Overcrowding",
        href = "#inventory-overcrowding",
        `data-subpage` = "inventory-overcrowding")
    )
  ),

  # Economics Section
  accordion_panel(
    "Economics",
    icon = bsicons::bs_icon("graph-up"),
    div(
      a("Household Income",
        href = "#economics-household-income",
        `data-subpage` = "economics-household-income"),
      br(),
      a("Poverty",
        href = "#economics-poverty",
        `data-subpage` = "economics-poverty"),
      br(),
      a("Employment",
        href = "#economics-employment",
        `data-subpage` = "economics-employment")
    )
  ),

  # Homeownership Section
  accordion_panel(
    "Homeownership",
    icon = bsicons::bs_icon("house-door"),
    div(
      a("Homeownership Rate",
        href = "#homeownership-rate",
        `data-subpage` = "homeownership-rate"),
      br(),
      a("Home Sales",
        href = "#homeownership-sales",
        `data-subpage` = "homeownership-sales"),
      br(),
      a("House Price Index",
        href = "#homeownership-hpi",
        `data-subpage` = "homeownership-hpi"),
      br(),
      a("Mortgages",
        href = "#homeownership-mortgages",
        `data-subpage` = "homeownership-mortgages")
    )
  ),

  # Rental Section
  accordion_panel(
    "Rental",
    icon = bsicons::bs_icon("key"),
    div(
      a("Rent",
        href = "#rental-rent",
        `data-subpage` = "rental-rent"),
      br(),
      a("Rental Vacancy",
        href = "#rental-vacancy",
        `data-subpage` = "rental-vacancy"),
      br(),
      a("Assisted Rentals",
        href = "#rental-assisted",
        `data-subpage` = "rental-assisted")
    )
  ),

  # Affordability Section
  accordion_panel(
    "Affordability",
    icon = bsicons::bs_icon("currency-dollar"),
    div(
      a("Cost Burden",
        href = "#affordability-cost-burden",
        `data-subpage` = "affordability-cost-burden"),
      br(),
      a("Rental Housing Gap",
        href = "#affordability-gap",
        `data-subpage` = "affordability-gap"),
      br(),
      a("HUD AMI Limits",
        href = "#affordability-ami",
        `data-subpage` = "affordability-ami")
    )
  ),

  # Instability Section
  accordion_panel(
    "Instability",
    icon = bsicons::bs_icon("exclamation-triangle"),
    div(
      a("Homelessness",
        href = "#instability-homelessness",
        `data-subpage` = "instability-homelessness")
    )
  ),

  # Economic Impact Calculators Section
  accordion_panel(
    "Economic Impact Calculators",
    icon = bsicons::bs_icon("calculator"),
    div(
      a("New Construction Calculator",
        href = "#calculators-new-construction",
        `data-subpage` = "calculators-new-construction"),
      br(),
      a("Renovation Calculator",
        href = "#calculators-renovation",
        `data-subpage` = "calculators-renovation")
    )
  )
  ) # Close accordion
) # Close tagList
```

## Column {.fill}

```{r}
#| echo: false

# Include the dashboard JavaScript - use inline to avoid CORS issues
js_content <- paste0(readLines("www/dashboard.js", warn = FALSE), collapse = "\n")
tags$script(HTML(js_content))
```

<div class="content-area">

::: {#intro-page .content-page .active}

```{r}
#| echo: false

# Banner with logo
div(
  class = "intro-banner",
  style = "text-align: center; margin-bottom: 3rem; padding: 3rem 2rem; background: linear-gradient(135deg, #011E41 0%, #40C0C0 100%); border-radius: 12px; color: white;",
  div(
    style = "margin-bottom: 1.5rem;",
    img(src = "www/hfv_primary_logo.svg", style = "height: 80px; max-width: 100%; object-fit: contain;")
  ),
  h1(style = "font-size: 2.5rem; font-weight: 700; margin-bottom: 1rem; color: white;", "SOURCEBOOK"),
  p(style = "font-size: 1.25rem; color: rgba(255, 255, 255, 0.9); margin: 0;", "Understand your community's housing needs.")
)
```

**Sourcebook** is HousingForward Virginia's online compendium of housing data. It collects, summarizes, and presents dozens of different data points to help users understand housing trends in their communities to advocate for and implement better housing solutions.

Housing and housing-related data is spread across multiple sources and can be time-consuming to clean up, analyze, and visualize. Sourcebook brings together the most important data points in one place to make that work simpler for you.

Sourcebook is an evolving and user-focused resource. We encourage you to contact us if there are particular features you would like to see, or data points that would be most helpful to your work.

## Getting Started

Use the sidebar to navigate through different housing data topics:

- **Demographics:** Population, age, race and ethnicity data
- **Economics:** Income, poverty, and employment trends
- **Inventory:** Housing stock, production, and characteristics
- **Homeownership & Rental:** Market trends and affordability
- **Affordability:** Cost burden and housing gaps
- **Instability:** Homelessness data
- **Economic Impact Calculators:** Tools to estimate job and economic growth

*Select your geographic area at the top of the sidebar, then explore the data topics that interest you most.*

:::

::: {#demographics-total-population .content-page}

```{r}
#| echo: false

h1("Total Population", style = "color: #011E41; font-weight: 700; font-size: 2.25rem; margin-bottom: 1.5rem; text-transform: uppercase; letter-spacing: 0.5px;")
```

The dashboards on this page include data on total population counts and components of population change. These trends help reveal how much, and for what reasons, population levels may be increasing or decreasing over time.

```{r}
#| echo: false

h2("Total population", style = "color: #011E41; font-weight: 600; font-size: 1.5rem; margin-top: 2rem; margin-bottom: 1rem;")
```

The 2020 Census was greatly impacted by the pandemic, as well as the use of differential privacy. The Demographics Research Group at the University of Virginia's Weldon Cooper Center advises data users to treat 2020 Census numbers with caution. But overall, they find that 2020 Census data "tends to be more reliable for larger areas and populations whereas in Virginia's smaller localities, data errors and distortions are much more common."

This dashboard shows annual population counts and percent changes. Data for 2010 and 2020 are from those years' Decennial Census counts; all other years use estimates from the Census Bureau's Population Estimates Program (PEP).

Data is available at the state, CBSA, and locality level.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://walkerke-total-pop.share.connect.posit.cloud/",
    src = "https://walkerke-total-pop.share.connect.posit.cloud/?geo=state",
    width = "100%",
    scrolling = "no",
    height = "70vh",
    frameborder = "0",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

```{r}
#| echo: false

h2("Total population change", style = "color: #011E41; font-weight: 600; font-size: 1.5rem; margin-top: 2rem; margin-bottom: 1rem;")
```

This dashboard shows annual population changes as both raw numbers and percentages, helping to understand growth patterns and demographic trends over time.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://walkerke-total-pop-chg.share.connect.posit.cloud/",
    src = "https://walkerke-total-pop-chg.share.connect.posit.cloud/?geo=state",
    width = "100%",
    scrolling = "no",
    height = "70vh",
    frameborder = "0",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

```{r}
#| echo: false

h2("Components of population change", style = "color: #011E41; font-weight: 600; font-size: 1.5rem; margin-top: 2rem; margin-bottom: 1rem;")
```

This dashboard breaks down annual population changes by three different components:

- Natural increases (births minus deaths),
- Domestic migration (net moves from in/out of state), and
- International migration (net moves from in/out of the country).

Data is available at the state, CBSA, and locality level.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://walkerke-pop-change.share.connect.posit.cloud/",
    src = "https://walkerke-pop-change.share.connect.posit.cloud/?geo=state",
    width = "100%",
    scrolling = "no",
    height = "70vh",
    frameborder = "0",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

```{r}
#| echo: false

h2("Additional resources", style = "color: #011E41; font-weight: 600; font-size: 1.5rem; margin-top: 2rem; margin-bottom: 1rem;")
```

- [U.S. Census Bureau](https://www.census.gov/)
- [Virginia adds more than 600,000 people since 2010](#)
- [UVA Weldon Cooper Center](https://demographics.coopercenter.org/)
- [State population growth slows, with most new residents in Northern Virginia](#)
- [Comparing 2020 Virginia population projections to the Census count](#)

__Data Sources__

> __Census Population Estimates Program (PEP)__
>
> Annual estimates of total population released by the U.S. Census Bureau. Available at locality level from 2010 to 2024. Estimates by age, race, and ethnicity also available, along with components of population change.
>
> __2020 Decennial Census__
>
> Official population counts from the 2020 Census, used as baseline data for population estimates.

:::

::: {#inventory-housing-type .content-page}

```{r}
#| echo: false

h1("Housing Type by Tenure", style = "color: #011E41; font-weight: 700; font-size: 2.25rem; margin-bottom: 1.5rem; text-transform: uppercase; letter-spacing: 0.5px;")
```

The dashboards on this page break down housing stock by the number of homes within each building. For example, a 1-unit residential building is a single-family home, while a 5-unit residential building is a small apartment complex. These data are helpful in understanding the makeup of a community's housing supply, overall density, and construction trends.

```{r}
#| echo: false

h2("Housing type by tenure", style = "color: #011E41; font-weight: 600; font-size: 1.5rem; margin-top: 2rem; margin-bottom: 1rem;")
```

This dashboard shows the current supply of occupied housing units among owners, renters, and all households, broken down by number of homes within each building.

All homes are classified into one of the following six categories:

- **Single-family (detached)** are homes with one living unit that does not share any walls with another home.
- **Single-family (attached)** are homes with one living unit that shares at least one wall with another home.
- **Small-scale multifamily** are homes in buildings with 2 to 19 total units. This includes duplexes, triplexes, and other similar buildings of three stories or fewer. This typically includes low-rise and mid-rise apartments.
- **Medium-scale multifamily** are homes in buildings with 20 to 49 total units. This typically includes low-rise and mid-rise apartments.
- **Large-scale multifamily** are homes in buildings with 50 or more total units. This typically includes mid-rise and high-rise apartments.
- **Mobile (manufactured) home** are factory-built homes that are fully built on a chassis. These homes are built to meet standards promulgated by the U.S. Department of Housing and Urban Development (the "HUD Code") and are distinct from modular/prefabricated homes.

Data is available at the state, CBSA, and locality level.

**NOTE:** The American Community Survey also includes an 'Other' category for certain housing types. These homes include boats, recreational vehicles (RVs), vans, and all other units that do not fall into one of the above categories. We have omitted this category because the share of these 'Other' units is insignificant (less than one percent) across all geographies in Virginia.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-housing-type-app.connect.posit.cloud/",
    width = "100%",
    height = "70vh",
    frameborder = "0",
    scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Additional Resources

[How Virginia communities are encouraging 'Missing Middle Housing'](#) - Planetizen

### Data Sources

#### American Community Survey

The American Community Survey is an ongoing survey program of the U.S. Census Bureau. The ACS collects information about the nation's social, economic, housing, and demographic characteristics on an annual basis. This information provides the most-up-to-date estimates between decennial censuses.

This section uses data from one ACS table:

**Table B25032:** Tenure by Units in Structure

The most recent data used for this section are the 2018-2022 5-year estimates. These estimates average all survey responses across this period to increase sample sizes and reduce margins of error.

The data contained in Sourcebook is intended for informational, educational and research uses. The information may not be used for commercial purposes or re-marketed. Any reproduction and distribution of this information must clearly identify HousingForward Virginia and Sourcebook as the provider of the information.

:::

::: {#demographics-race-ethnicity .content-page}

# Race and Ethnicity

Population by race and Hispanic or Latino heritage.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-race-ethnicity.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Population estimates by race and ethnicity from the U.S. Census Bureau.

:::

::: {#demographics-age .content-page}

# Age

Population data by age groups.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://walkerke-dem-age.share.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Age distribution data from the U.S. Census Bureau.

:::

::: {#demographics-household-type .content-page}

# Household Type

Relationships of people living under the same roof.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-household-type.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Household composition data from the U.S. Census Bureau.

:::

::: {#demographics-household-size .content-page}

# Household Size

Number of persons per household.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-household-size.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Household size distribution from the U.S. Census Bureau.

:::

::: {#economics-household-income .content-page}

# Household Income

Income by tenure, age, race and ethnicity.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-household-income.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Household income data from the U.S. Census Bureau.

:::

::: {#economics-poverty .content-page}

# Poverty

Poverty rates by age, race and ethnicity.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-poverty.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Poverty status data from the U.S. Census Bureau.

:::

::: {#economics-employment .content-page}

# Employment

Job levels, unemployment rates, and jobs-housing ratios.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-employment.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### Bureau of Labor Statistics

Employment and unemployment data from federal and state labor statistics.

:::

::: {#inventory-housing-production .content-page}

# Housing Production

Building permits by structure type.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-housing-production.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### U.S. Census Bureau Building Permits Survey

New construction authorized by building permits.

:::

::: {#inventory-housing-age .content-page}

# Housing Age

Housing stock by tenure and year built.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-housing-age.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Year structure built data from the U.S. Census Bureau.

:::

::: {#inventory-housing-characteristics .content-page}

# Housing Characteristics

Physical characteristics of housing stock.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-housing-characteristics.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Housing unit characteristics from the U.S. Census Bureau.

:::

::: {#inventory-overcrowding .content-page}

# Overcrowding

Number of persons per room.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-overcrowding.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Occupancy characteristics from the U.S. Census Bureau.

:::

::: {#homeownership-rate .content-page}

# Homeownership Rate

Share of homeowners by age, race and ethnicity.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-homeownership-rate.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Housing tenure data from the U.S. Census Bureau.

:::

::: {#homeownership-sales .content-page}

# Home Sales

For-sale prices and inventory trends.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-home-sales.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### Virginia Association of Realtors

Home sales and pricing data from local real estate markets.

:::

::: {#homeownership-hpi .content-page}

# House Price Index

Historic-to-present Federal Housing Finance Agency HPI.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-hpi.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### Federal Housing Finance Agency

House Price Index data showing price changes over time.

:::

::: {#homeownership-mortgages .content-page}

# Mortgages

Loan originations and denials by race and ethnicity.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-mortgages.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### Home Mortgage Disclosure Act (HMDA)

Mortgage lending data from the Consumer Financial Protection Bureau.

:::

::: {#rental-rent .content-page}

# Rent

Gross rent averages and spread.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-rent.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Gross rent data from the U.S. Census Bureau.

:::

::: {#rental-vacancy .content-page}

# Rental Vacancy

Vacancy rates for rental properties.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-rental-vacancy.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Housing vacancy data from the U.S. Census Bureau.

:::

::: {#rental-assisted .content-page}

# Assisted Rentals

Homes with dedicated public subsidies.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-assisted-rentals.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### HUD and Virginia Housing

Subsidized housing data from federal and state agencies.

:::

::: {#affordability-cost-burden .content-page}

# Housing Cost Burden

Cost burden by income, race and ethnicity.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-cost-burden.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### American Community Survey

Housing cost burden data from the U.S. Census Bureau.

:::

::: {#affordability-gap .content-page}

# Rental Housing Gap

Affordability of current supply by income.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-housing-gap.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### National Low Income Housing Coalition

Housing affordability gap analysis.

:::

::: {#affordability-ami .content-page}

# HUD AMI Limits

Income limits used by affordable housing programs.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-ami-limits.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### U.S. Department of Housing and Urban Development

Area Median Income limits for affordable housing programs.

:::

::: {#instability-homelessness .content-page}

# Homelessness

Point-in-Time homelessness for Continuum of Care regions.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-homelessness.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### U.S. Department of Housing and Urban Development

Point-in-Time count data from Continuum of Care regions.

:::

::: {#calculators-new-construction .content-page}

# New Construction Calculator

Estimate job and economic growth from new construction.

The Virginia Center for Housing Research developed these calculators to estimate the economic impact of housing activity on local economies.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-new-construction-calc.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### Virginia Center for Housing Research

Economic impact methodology based on regional economic modeling.

:::

::: {#calculators-renovation .content-page}

# Renovation Calculator

Estimate job and economic growth from major rehab projects.

The Virginia Center for Housing Research developed these calculators to estimate the economic impact of housing activity on local economies.

```{r}
#| echo: false

div(
  class = "app-container",
  tags$iframe(
    `data-base-url` = "https://example-renovation-calc.connect.posit.cloud/",
    width = "100%", height = "70vh", frameborder = "0", scrolling = "no",
    style = "border: 1px solid #e0e0e0; border-radius: 8px;"
  )
)
```

### Data Sources

#### Virginia Center for Housing Research

Economic impact methodology for renovation and rehabilitation projects.

:::

</div>
